Viscous Transport in Eroding Porous Media

### 2019-09-30 docs/transport/erosion_transport.tex
did revions to abstract

\begin{abstract} 
  We extend upon our previous work, [Journal of Computational Physics,
  {\bf 375}:1--21, 2018], to simulate dense suspensions of
  fluid-mechanical erosion of two-dimensional erosion of porous media.
  The method combines a boundary integral equation (BIE) fluid solver
  and a numerically stable time stepping method for the evolution of the
  eroding bodies. Originally, the eroding bodies had to be sufficiently
  separated to guarantee that the trapezoid rule provided a sufficient
  level of accuracy. In this work, we develop resolve interactions
  between nearly touching bodies with a Barycentric quadrature rule
  whose error is independent of the geometry.  Since the Barycentric
  quadrature rule is computationally expensive, it is only used when
  necessary, and the spectrally accurate trapezoid rule is used
  otherwise. Our final fluid solver only requires $\mathcal{O}(N)$
  iterations per time step. Next, we simulate and analyze transport
  through eroded porous geometries.  Our results demonstrate the effects
  of erosion on tortuosity, dispersion, and pore size distributions.
\end{abstract}

>>>>

\begin{abstract} 
  We extend our previous work, [{\em Journal of Computational Physics},
  {\bf 375}:1--21, 2018], to simulate fluid-mechanical erosion of
  two-dimensional porous media with nearly-touching grains.  The method
  continues to use a boundary integral equation (BIE) method to solve
  the fluid equations and to compute the erosion rate, and a stable
  second-order time stepping method to erode the grains.  In our
  original work, we required that the eroding grains were sufficiently
  separated to guarantee that the trapezoid rule provides a sufficient
  amount of accuracy. We now remove this restriction by introducing a
  Barycentric quadrature rule whose error is bounded independent of the
  geometry.  The Barycentric quadrature rule is computationally
  expensive, so it is only used when necessary, and the spectrally
  accurate trapezoid rule is used otherwise. We also simulate and
  analyze transport through eroded porous geometries.  By using the
  Barycentric quadrature rule, the analysis examines flow both in the
  fast and slow regions with high-order accuracy. Our results
  demonstrate the effects of erosion on tortuosity, dispersion, and pore
  size distributions.
\end{abstract}
